---
subtitle: "Exposition Pipes"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Exposition Pipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(simplePipes)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/simplePipes")}
library(simplePipes)
```

## Exposition Pipes

Exposition pipes indicate a data set to be used for other commands (or pipes), replacing the need for a `with` command.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Input Data

First, name a few variables and assign arrays of values back them. Then create a `frame` that holds both variables.

```{r}
variable1 <- c(1,2,6,8,9,15)
variable2 <- c(4,3,5,6,4,10)
frame <- data.frame(variable1,variable2)
```

### Standard R Syntax

In standard R syntax, use `with` to select the data `frame`, then get the `mean` of `variable2`.

```{r}
with(frame,mean(variable2))
```

### Forward Exposition Pipe

Using the forward exposition pipe, select the data `frame`, then get the `mean` of `variable2`.

```{r}
frame %$>% mean(variable2)
```

Going a step further by chaining in a basic pipe, select the data `frame`, then identify `variable2` and get its `mean`.

```{r}
frame %$>% variable2 %>% mean
```

### Backward Exposition Pipe

Using the backward exposition pipe, get the `mean` of `variable2` using the data `frame`. 

```{r}
mean(variable2) %<$% frame
```

Going a step further by chaining in a basic pipe, get the `mean` of `variable2` using the data `frame`.

```{r}
mean %<% variable2 %<$% frame
```
