---
subtitle: "Through Pipes"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Through Pipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
# suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(simplePipes)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/simplePipes")
}
library(simplePipes)
```

## Through Pipes

Through pipes chain a series of commands, allowing the first piped values to be used as input in multiple subsequent commands (rather than just the next command in the chain). They expand the functionality of tee pipes.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Input Data

First, name a `variable` and assign an array of values back to it.

```{r}
variable <- c(1, 2, 6, 8, 9, 15)
```

Though it's not commonly demonstrated, R does permit forward assignment of vales to a `variable`.

```{r}
c(1, 2, 6, 8, 9, 15) -> variable
```

### Standard R Syntax

In standard R syntax, get the `mean` of the `variable` and then get the `sd` of the `variable`.

```{r}
mean(variable)
sd(variable)
```

### Native Pipe

After version 4.1, R includes a native forward pipe and shorthand syntax for anonymous functions. With R 4.3, curly braces extend this functionality.

Here, the anonymous function is used to create a placeholder (`x`) and then print the `mean` of the `variable` and then get the `sd` of the `variable`. 

```{r}
variable |> (\(.) { print(mean(.)); . } )() |> sd()
```

### Forward Through Pipe

Using the forward through pipe, identify the `variable` and then get both its `mean` and `sd`.

```{r}
variable %.>>% mean(.) %.>>% sd(.)
```
