---
subtitle: "Wype Pipes"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Wye Pipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
# suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(simplePipes)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/simplePipes")
}
library(simplePipes)
```

## Wye Pipes

Wye pipes chain a first command to two (or more) subsequent commands simultaneously. They take the place of multiple pipes.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Input Data

First, name a `variable` and assign an array of values back to it.

```{r}
variable <- c(1, 2, 6, 8, 9, 15)
```

Though it's not commonly demonstrated, R does permit forward assignment of vales to a `variable`.

```{r}
c(1, 2, 6, 8, 9, 15) -> variable
```

### Standard R Syntax

In standard R syntax, get the `mean` of the `variable` and also get the `sd` of the `variable`.

```{r}
mean(variable)
sd(variable)
```

### Native Pipe

After version 4.1, R includes a native forward pipe and shorthand syntax for anonymous functions. 


Here, the anonymous function is used to create a dot placeholder (`x`) and then to pipe into multiple functions, like `mean` and `sd`.

```{r}
variable |> (\(x) c(mean(x), sd(x)))()
```

### Forward Wye Pipe

Using the forward wye pipe, identify the `variable` and then get both its `mean` and `sd`.

```{r}
variable %Y>% c(mean, sd)
```

### Backward Wye Pipe

Using the backward wye pipe, get both the `mean` and `sd` of the `variable`.

```{r}
c(mean, sd) %<Y% variable
```
