---
subtitle: "Basic Pipes"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Basic Pipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
# suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(simplePipes)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/simplePipes")
}
library(simplePipes)
```

## Basic Pipes

Basic pipes are used for chaining (rather than nesting) commands. They assume that the piped values are the first and only arguments passed to the next command.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Input Data

First, name a `variable` and assign an array of values back to it.

```{r}
variable <- c(1, 2, 6, 8, 9, 15)
```

Though it's not commonly demonstrated, R does permit forward assignment of vales to a `variable`.

```{r}
c(1, 2, 6, 8, 9, 15) -> variable
```

### Standard R Syntax

In standard R syntax, get the `mean` of the `variable`.

```{r}
mean(variable)
```

### Native Pipe

After version 4.1, R includes a native forward pipe. Here, `variable` is piped directly to get its `mean`.

```{r}
variable |> mean()
```

### Forward Basic Pipe

Using the forward basic pipe, identify the `variable` and then get its `mean`.

```{r}
variable %>% mean()
```

### Backward Basic Pipe

Using the backward basic pipe, get the `mean` of the `variable`.

```{r}
mean %<% variable
```
