---
subtitle: "Dot Pipes"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Dot Pipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(simplePipes)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/simplePipes")}
library(simplePipes)
```

## Dot Pipes

Simple dot pipes also chain commands but expand on basic pipes by allowing the piped values to be placed anywhere in the next command in the chain. They expand the functionality of both basic and wye pipes.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Input Data

First, name a `variable` and assign an array of values back to it.

```{r}
variable <- c(1,2,6,8,9,15)
```

### Standard R Syntax

In standard R syntax, get the `mean` of the `variable` (while specifying additional parameters).

```{r}
mean(variable,trim=.2)
```

Going a step further, get both the `mean` and the `sd` of the `variable` (while specifying additional parameters).

```{r}
c(mean(variable,trim=.2), sd(variable))
```

### Forward Dot Pipe

Using the forward dot pipe, identify the `variable` and get its `mean` (while also specifying additional parameters).

```{r}
variable %.>% mean(.,trim=.2)
```

Going a step further, identify the `variable` and then get both its `mean` and `sd` (while also specifying additional parameters).

```{r}
variable %.>% {c(mean(.,trim=.2),sd(.))}
```

### Backward Dot Pipe

Using the backward dot pipe, get the `mean`  of the `variable` (while also specifying additional parameters).

```{r}
mean(.,trim=.2) %<.% variable
```

Going a step further, get both the `mean` and `sd` of the `variable` (while also specifying additional parameters).

```{r}
{c(mean(.,trim=.2),sd(.))} %<.% variable
```
