---
subtitle: "Exposition Pipes"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Exposition Pipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
# suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(simplePipes)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/simplePipes")
}
library(simplePipes)
```

## Exposition Pipes

Exposition pipes indicate a data set to be used for other commands (or pipes), replacing the need for a `with` command.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Input Data

First, name a few variables and assign arrays of values back them. Then create a `frame` that holds both variables.

```{r}
variable1 <- c(1, 2, 6, 8, 9, 15)
variable2 <- c(4, 3, 5, 6, 4, 10)
frame <- data.frame(variable1, variable2)
```

Though it's not commonly demonstrated, R does permit forward assignment of vales to a `variable`.

```{r}
c(1, 2, 6, 8, 9, 15) -> variable
```

### Standard R Syntax

In standard R syntax, use `with` to select the data `frame`, then get the `mean` of `variable2`.

```{r}
with(frame, mean(variable2))
```

### Native Pipe

After version 4.1, R includes a native forward pipe and shorthand syntax for anonymous functions. With R 4.3, curly braces extend this functionality.

Here, the anonymous function is used to create a placeholder (`x`) and then to pipe into the `with` command to get the `mean` of `variable2`.

```{r}
frame |> (\(x) with(x, mean(variable2)))()
```

Taking it a step further, a pipe can be created within the anonymous function from above to take `variable2` and get its `mean`.

```{r}
frame |> (\(x) with(x, { variable2 |> mean() } ))()
```

### Forward Exposition Pipe

Using the forward exposition pipe, select the data `frame`, then get the `mean` of `variable2`.

```{r}
frame %$>% mean(variable2)
```

Going a step further by chaining in a basic pipe, select the data `frame`, then identify `variable2` and get its `mean`.

```{r}
frame %$>% variable2 %>% mean()
```

### Backward Exposition Pipe

Using the backward exposition pipe, get the `mean` of `variable2` using the data `frame`. 

```{r}
mean(variable2) %<$% frame
```

Going a step further by chaining in a basic pipe, get the `mean` of `variable2` using the data `frame`.

```{r}
mean %<% variable2 %<$% frame
```
