---
subtitle: "Tee Pipes"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Tee Pipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
# suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(simplePipes)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/simplePipes")
}
library(simplePipes)
```

## Tee Pipes

Tee pipes also involve chaining commands but are used when an intermediate command produces output (such as a plot). The intermediate command also acts as a flow-through to a third command in the chain.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Input Data

First, name a `variable` and assign an array of values back to it.

```{r}
variable <- c(1, 2, 6, 8, 9, 15)
```

Though it's not commonly demonstrated, R does permit forward assignment of vales to a `variable`.

```{r}
c(1, 2, 6, 8, 9, 15) -> variable
```

### Standard R Syntax

In standard R syntax, `plot` the `variable` and then get the `mean` of the `variable`.

```{r,Standard-Plot}
plot(variable)
mean(variable)
```

### Native Pipe

After version 4.1, R includes a native forward pipe and shorthand syntax for anonymous functions. With R 4.3, curly braces extend this functionality.

Here, the anonymous function is used to create a placeholder (`x`) and then to `plot` the `variable` and then get the `mean` of the `variable`. (For functions that print output rather than plot, additional manipulation is needed. See the implementation of through pipes.)

```{r}
variable |> (\(x) { plot(x); x } )() |> mean()
```

### Forward Tee Pipe

Using the forward tee pipe (and chaining in a basic pipe), identify the `variable` and then `plot` it and get its `mean`.

```{r,Forward-Tee-Plot}
variable %T>% plot %>% mean
```

### Backward Tee Pipe

Using the backward tee pipe (and chaining in a basic pipe), `plot` the `variable` and then get its `mean`.

```{r,Backward-Tee-Plot}
plot %<T% variable %>% mean
```
