---
subtitle: "Tee Pipes"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Tee Pipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(simplePipes)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/simplePipes")}
library(simplePipes)
```

## Tee Pipes

Tee pipes also involve chaining commands but are used when an intermediate command produces output (such as a plot). The intermediate command also acts as a flow-through to a third command in the chain.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Input Data

First, name a `variable` and assign an array of values back to it.

```{r}
variable <- c(1,2,6,8,9,15)
```

### Standard R Syntax

In standard R syntax, `plot` the `variable` and then get the `mean` of the `variable`.

```{r,Standard-Plot}
plot(variable); mean(variable)
```

### Forward Tee Pipe

Using the forward tee pipe (and chaining in a basic pipe), identify the `variable` and then `plot` it and get its `mean`.

```{r,Forward-Tee-Plot}
variable %T>% plot %>% mean
```

### Backward Tee Pipe

Using the backward tee pipe (and chaining in a basic pipe), `plot` the `variable` and then get its `mean`.

```{r,Backward-Tee-Plot}
plot %<T% variable %>% mean
```
