---
title: "Assignment Pipes"
author: "Craig A. Wendorf"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Assignment Pipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(simplePipes)
```

## Assignment Pipes

### Input Data

First, name a `variable` and assign an array of values back to it.

```{r}
variable <- c(1,2,6,8,9,15)
```

### Standard R Syntax

In standard R syntax, name a `variable` already in use, get the `mean` of the `variable` and assign the value back to the variable. Display the resulting value.

```{r}
variable <- mean(variable)
variable
```

### Compound Assignment Pipe

Using the compound assignment pipe, identify a `variable` already in use and assign its `mean` back to the variable. Display the resulting value.

```{r}
variable %<>% mean
variable
```
